Types for R, Empirically Designed and Evaluated

### 2020-05-07 paper/main.tex
Fix contractr introduction

\subsection{contractr}
\label{sec:contractr}
contractr is an R package that implements our type system for the R package
ecosystem. It adds contracts to package functions for type-checking function
arguments and results. On contract failure, it reports a warning message with
the package name, function name, argument name and position, expected type
(according to the type declaration), actual type (of the value observed), and a
stack trace for the called function.

contractr is implemented in 434 R LOC and 2358 C++ LOC. It has been designed and
tested with GNU R-3.5.0 but it also works with recent R releases. The package
has been hardened with a battery of 400 test cases and battle-tested with sanity
checking for the 500 packages for which we generate type signatures and 12,000
packages against which we evaluate them.

contractr works by modifying function definitions to insert calls to our
type-checking function. When the modified function is called, our type-checking
function gets executed first.  The type-checker is invoked on each call to the
function on all of its arguments and return value.

>>>>

\subsection{contractr}
\label{sec:contractr}
\emph{contractr} is an R package that implements our type system for the R
package ecosystem. It adds contracts to package functions for type-checking
arguments and results on function calls. On contract failure, it reports a type
mismatch warning with the package name, function name, argument name, argument
position, expected type signature, actual type signature of the value observed,
and a stack trace for the called function. \emph{contractr} works by modifying
function definition to insert a call to the type-checking function. When the
modified function is called, the type-checking function is invoked on the
modified function's arguments and return value.

\emph{contractr} is implemented in 434 R LOC and 2358 C++ LOC. The core
implementation is in C++ to keep the runtime overhead low. It been designed and
tested with GNU R-3.5.0 but it also works with recent versions of R. It has been
hardened with a battery of 400 test cases. We have used it extensively during
the course of this work; firstly, for sanity checking of XXX type signatures
generated for the XXX packages during the development phase, and secondly, for
assessing the quality of these type signatures on XXX packages during the
evaluation phase.
